Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-07-13 src/tex/ms.tex
address comment 2 from referee #2 (definition of S_thresh)

For \textit{runaway} planets, i.e., all planets receiving a dayside-averaged instellation exceeding a threshold of $S_\mathrm{thresh} = \var{injectedSthresh}$, we assume an inflated transit radius due to a steam atmosphere.
While the actual instellation threshold for a runaway climate depends on planetary albedo, surface gravity, and clouds~\citep{2019Icar..317..583P,Turbet2021,Pierrehumbert2022}, this value was found to be a typical limit for the flux a planet can emit in a runaway greenhouse situation~\citep{Goldblatt2013,Kopparapu2013,Leconte2013,Hamano2015,2017JGRE..122.1458S,2019ApJ...875...31K,Boukrouche2021,2021JGRE..12606711L}.

>>>>

\rev{We consider as \textit{runaway} planets those planets that absorb a stellar flux higher than a} dayside-averaged \rev{threshold instellation $S_\mathrm{thresh}$}.
\rev{For all planets receiving an instellation exceeding} $S_\mathrm{thresh} = \var{injectedSthresh}$, we assume an inflated transit radius due to a steam atmosphere.
While the actual instellation threshold for a runaway climate depends on planetary albedo, surface gravity, and clouds~\citep{2019Icar..317..583P,Turbet2021,Pierrehumbert2022}, this value was found to be a typical limit for the flux a planet can emit in a runaway greenhouse situation~\citep{Goldblatt2013,Kopparapu2013,Leconte2013,Hamano2015,2017JGRE..122.1458S,2019ApJ...875...31K,Boukrouche2021,2021JGRE..12606711L}.
